

%%% Choose a language %%%

\newif\ifEN
\ENtrue   % uncomment this for english
%\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
%\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
%\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Financial News Sentiment Analysis}
\def\ThesisAuthor{Václav Stibor}
\def\YearSubmitted{2024}

% department assigned to the thesis
\def\Department{Department of Software Engineering}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

\def\Supervisor{doc. RNDr. Irena Holubová, Ph.D.}
\def\SupervisorsDepartment{Department of Software Engineering}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{\xxx{study branch}}

\def\Dedication{%
    I would like to dedicate this thesis to my family and friends who have supported me throughout my studies. Special thanks to my supervisor doc. RNDr. Irena Holubová, Ph.D. for her expertise and guidance during the development of this work. To all who have assisted me, I sincerely appreciate your support.

    Additionally, I am grateful for the consultations provided by Mgr. Petr Škoda, Ph.D., and Ing. Pavel Koupil, Ph.D. contributed to this thesis's improved outcomes.
}

\def\AbstractEN{%
{
    In the current era of information overload, tracking associations and comprehending media and online news content, especially for investment purposes, is becoming increasingly demanding. This thesis addresses the challenge by developing an application that evaluates sentiment analysis and visualises connections between companies and news articles. The cornerstone of the application is the extraction of data from news articles, sentiment analysis of the extracted entities, and the provision of this information as an indicator of potential future influences on a company's stock price. The application is designed to be easy to use and intuitive, allowing users to navigate to the articles and perform their analysis to verify the values provided by the application.
}
% ABSTRACT IS NOT A COPY OF YOUR THESIS ASSIGNMENT! < 500 Words
}

\def\AbstractCS{%
V dnešní době přehlcené informacemi se sledování souvislostí a porozumění obsahu médií a online zpráv, zejména pro investiční účely, se stává stále náročnějším. Tato práce se zabývá daným problémem a vývojem aplikace, která vyhodnocuje analýzu sentimentu a vizualizuje spojení mezi společnostmi a zpravodajskými články. Základem aplikace je extrakce dat ze zpravodajských článků, analýza sentimentu extrahovaných entit a poskytování těchto informací jako indikátor možných budoucích vlivů na cenu akcií společnosti. Aplikace je navržena tak, aby byla snadno použitelná a intuitivní, což umožňuje uživatelům navigovat k článkům a provádět tak i vlastní analýzu pro ověření hodnot poskytovaných aplikací.
}

%\xxx{You will need to submit both Czech and English abstract to the SIS, no matter what language you use in the thesis. If writing in English, translate the contents of \texttt{\textbackslash{}AbstractEN} into this field. In case you do not speak czech, your supervisor should be able to help you with the translation.}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{%
{entity-level} {sentiment analysis} {news} {stock market}
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{\xxx{Thesis title in English}}
\def\DepartmentEN{\xxx{Name of the department in English}}
\def\DeptTypeEN{\xxx{Department}}
\def\SupervisorsDepartmentEN{\xxx{Superdepartment}}
\def\StudyProgrammeEN{\xxx{study programme}}
\def\StudyBranchEN{\xxx{study branch}}
\def\KeywordsEN{%
\xxx{{key} {words}}
}
\fi
